%CameronResumeDev.tex
\author{Cameron Dershem}                    %top matter
\title{Cameron Dershem Resume}              %top matter
\documentclass[letterpaper]{article}        %document class
\usepackage[
  letterpaper,
  top=1in,
  bottom=0.5in,
  %right=1in,
  %left=1in,
  ]{geometry}                     %margins
\usepackage{enumitem}
\usepackage{libertine}
\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault}    %sets sans serif
\usepackage{fancyhdr}
\pagestyle{fancy}                           %header
\pagenumbering{gobble}                      %removes page numbers
\setlength{\parindent}{0pt}                 %removes indents
\usepackage{verbatim}                       %allows comments
\renewcommand{\headrulewidth}{0pt}          %removes header rule
\setlength{\headheight}{30.0pt}             %gives header room
\setlength{\headsep}{-1.0em}                %removes space below header
\setitemize{%                               %condenses itemized lists
  noitemsep,
  topsep=0pt,
  parsep=0pt,
  partopsep=0pt,
  leftmargin=1em,
  labelsep=2pt
  }%label=~}
\setdescription{%                           %condenses description lists
  noitemsep,
  topsep=0pt,
  parsep=0pt,
  partopsep=0pt,
  labelsep=2pt}
\renewcommand{\descriptionlabel}[1]{\textbf{\textsc{{#1} --}}}
\usepackage{array}                          %allows bold in tabular
\usepackage{microtype}
\usepackage{multicol}
\setlength\multicolsep{0pt}
%\setlength{\columnseprule}{1pt}

\newcommand{\JobHeader}[4]{%                %job/school header
  \textls{\textbf{\textsc{{#1}}}%
  \hfill
  \textsc{#2}}
  \\%
  \textsc{#3}
  \hfill
  \textsc{#4}
  }

\newcommand{\sectionHeader}[1]{%            %header for sections
  \vspace{0.4em}%
  \hrule%
  \vspace{0.4em}%
  \textls{{\textbf{\textsc{#1}}\dotfill}}%
  }

\newcommand{\objective}[1]{%
  \hrule
  \vspace{0.4em}
  \textls{{\textbf{\textsc{OBJECTIVE:\@ }}}}{#1}}%

\usepackage{etoolbox}                       %used to toggle Dev/Generic
\newbool{isGeneric}
% \booltrue{isGeneric}
\boolfalse{isGeneric}

\newcommand{\showGeneric}[1]{%
  \ifbool{isGeneric}{{#1}}{}}

\newcommand{\showDev}[1]{%
  \ifbool{isGeneric}{}{{#1}}}

\fancyhead[L]{%
  \fontsize{24.88}{10pt}
  \selectfont \textsc{Cameron Dershem}}
\fancyhead[R]{%
  cldershem@gmail.com \textbar{}
  312.361.0322 \textbar{}
  Indianapolis, IN
  \\
  homelessgaffer.com \textbar{}
  github.com/cldershem%
  }

\begin{document}                            % actual content starts here

\objective{%
  To successfully transition careers into application development %
  by obtaining an entry-level position to gain experience and %
  knowledge.  Seeking new challenges and stability by %
  leveraging an enthusiasm for efficiency and simplicity while %
  finding and building solutions.%
  }%
\sectionHeader{SKILLS \& INTERESTS}
  \begin{multicols}{3}
    \sectionHeader{OSes:}
      \begin{itemize}
        \item Linux \hfill advanced 
        \item Windows \hfill intermediate
        \item OS X \hfill intermediate
        \item Chrome OS \hfill expert
        \item Android \hfill expert
        \item Ubuntu \hfill advanced
      \end{itemize}
    \sectionHeader{Languages:}
      \begin{itemize}
        \item Python \hfill intermediate
        \item HTML \hfill intermediate
        \item CSS \hfill intermediate
        \item LESS \hfill intermediate
        \item JavaScript
        \item \LaTeX{} \hfill intermediate
        \item Bash
        \item PHP beginner
        \item C \hfill novice
      \end{itemize}
    \sectionHeader{Frameworks:}
      \begin{itemize}
        \item Flask \hfill 1 year
      \end{itemize}
    \sectionHeader{Database:}
      \begin{itemize}
        \item MySQL
        \item MongoDB
      \end{itemize}
    \sectionHeader{Tools:}
      \begin{itemize}
        \item Vim
        \item Git
        \item Adobe CS
      \end{itemize}

    \sectionHeader{Other:}
      \begin{itemize}
        \item quick learner
        \item always learning
        \item ability to teach
        \item Strong troubleshooting skills
        \item solution focused
        \item focused on efficiency
        \item multitasking
        \item keep up morale while doing just about anything
        \item takes direction
        \item ability to lead
        \item Sales
        \item Customer service, support, \& training
        \item Testing, troubleshooting, reporting bugs
        \item Designed and implemented inventory control systems
        \item improved POS
        \item improve communications
        \item Trained management, employees, peers, and clients
        \item Developed training methods and materials
        \item manage rentals dept.
        \item lighting
        \item management - personnel, records, budget
        \item crew safety
        \item designed and distributed power and lighting
        \item promoted departmental communication
        \item Student and faculty support
        \item Occasionally taught
        \item Projected film
        \item equipment acquisition, inventory, maintenance, service, troubleshooting, bug reporting
      \end{itemize}
  \end{multicols}

\sectionHeader{PERSONAL \& PUBLIC PROJECTS}

  \begin{description}
    \item[Battleship] Multiplayer game written in Python---eventually to be rewritten as a web app
    \item[HomelessGaffer.com] Simple CMS written in Python using Flask---deployed using git-hooks
  \end{description}

\sectionHeader{EDUCATION}

  \JobHeader{Columbia College Chicago}{Chicago, IL}{B.A. Film/Video---Cinematography Concentration}{2003--2008}

\sectionHeader{EXPERIENCE}

  \JobHeader{MarketStar}{Indianapolis, IN}{Google Specialist}{November 2012--December 2012}
    \begin{itemize}
      \item Wordy words Designed and implemented inventory control system along with improved productivity, efficiency, communication, etc. by an order of magnitude.
    \end{itemize}

  \JobHeader{Orange 20 Bikes}{Los Angeles, CA}{IT Management \& Inventory Control}{October 2011--June 2012}
    \begin{itemize}
      \item Designed and implemented inventory control system along with improved productivity, efficiency, communication, etc. by an order of magnitude.
    \end{itemize}

  \JobHeader{Camadeus Film Technologies, Inc}{Los Angeles, CA}{Rental Agent}{June 2010--September 2011}
    \begin{itemize}
      \item More words Designed and implemented inventory control system along with improved productivity, efficiency, communication, etc. by an order of magnitude.
    \end{itemize}

  \JobHeader{Various Motion Picture Productions}{Chicago, IL \& Los Angeles, CA}{Freelance Gaffer \& Best Boy Electric}{June 2002--June 2010}
    \begin{itemize}
      \item Word word word words Designed and implemented inventory control system along with improved productivity, efficiency, communication, etc. by an order of magnitude.
    \end{itemize}

  \JobHeader{Columbia College Chicago}{Chicago, IL}{Teacher's Assistant \& Projectionist}{August 2003--June 2006}
    \begin{itemize}
      \item Double words Designed and implemented inventory control system along with improved productivity, efficiency, communication, etc. by an order of magnitude.
    \end{itemize}

\end{document}
